Hybrid platforms and bargaining power

### 2023-12-06 src/paper/application.tex
Expand intro of logit model

Let us now add more structure to the model, and microfound the profit function $\Pi$.
The model in this section is heavily inspired by the logit-like demand structure and hybrid platform setting in \textcite{anderson2021hybrid}.
The setting can be thought of as a (possibly hybrid) platform market with monopolistically competing fringe firms.

@@

Imagine that there is a unit mass of consumers, looking to buy one product each.
They choose from a continuum of products, indexed by $i$.
Customer $j$ derives the following utility from buying product $i$:
\begin{align*}
    u^F_{ij} = v^F_i - p^F_i + \mu\epsilon^F_{ij},
\end{align*}
where $v^F_i$ is the value of product $i$, $p^F_i$ is its price, and $\epsilon^F_{ij}$ is an idiosyncratic taste shock.
Throughout this section I assume that the value of each product is the same: $v^F_i = v^F$.
This is to simplify the analysis, but is not crucial for getting the results.  % TODO: look into relaxing this assumption

>>>>

Let us now add more structure to the model, place the function $\Pi$ on more solid microfoundations.
The modeling strategy is heavily inspired by the logit-like demand structure and hybrid platform setting of \textcite{anderson2021hybrid}.
The setting can be thought of as a (possibly hybrid) platform market with monopolistically competing fringe firms.

In the main model, I consider the case when the total profit function only includes the sales of the platform's and fringe firms' products.
That is, the platform does not charge any entry fees to the consumers.
Here, I consider two variants of the model: a benchmark where the platform can unilaterally commit to any entry fee, and a bargaining model where the platform and the fringe firms negotiate over the distribution of profits.

As an extension, I also examine what happens if the platform is able to extract consumer surplus by charging a flat entry fee, and the platform and the firms bargain over this larger sum.
Furthermore, I also consider the case of two-sided bargaining, where the consumers also participate in the negotiation over the value produced.

Throughout the analysis, I treat the product variety of the platform and the number of consumers as exogenous, and focus on the equilibrium number of fringe firms.
Nevertheless, the results regarding equilibrium platform profits and consumer surplus are somewhat indicative of the potential general equilibrium behavior of the former two, as well.

@@

Imagine that there is a unit mass of consumers, looking to buy one product each.
They choose from a continuum of products, indexed by $i$.
Customer $j$ derives the following utility from buying product $i$:
\begin{align*}
    u^F_{ij} = v^F_i - p^F_i + \mu\epsilon^F_{ij},
\end{align*}
where $v^F_i$ is the value of product $i$, $p^F_i$ is its price, and $\epsilon^F_{ij}$ is an idiosyncratic taste shock.
Throughout this section I assume that the value of each product is the same: $v^F_i = v^F$.
This is to simplify the analysis, but is not crucial for the results.  % TODO: look into relaxing this assumption
